---
title: "HW2 Molotkov Ivan"
output:
  html_document:
    df_print: paged
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(glue)
```

## 1. Create our deck using R dataframe

```{r}
deck <- read.csv('https://raw.githubusercontent.com/AntonZamyatin/r-course/main/HW2/deck.csv')
```

## 2. Player's hands

```{r}
player_hand <- data.frame()
dealer_hand <- data.frame()
```

## 3. shuffle_deck function

Here I shuffle global deck.

```{r}
shuffle_deck <- function() {
  deck <<- deck[sample(1:nrow(deck)), ]
}
```

## 4. Give a card to a player

```{r}
give_card <- function(pl) {
  if (pl == "player") {
    player_hand <<- rbind(player_hand, deck[1, ])
    deck <<- deck[2:nrow(deck), ]
  } else if (pl == "dealer") {
    dealer_hand <<- rbind(dealer_hand, deck[1, ])
    deck <<- deck[2:nrow(deck), ]
  }
}
```

## 5. Chances to win

If player's score is greater than 21, they lose.

Otherwise, If player's score is greater than the dealer's, player wins. 

Otherwise, we calculate the probability to win after the next deal.

```{r}
get_chances <- function() {
  if (sum(player_hand$value) > 21) {
    return(0)
  } else if (sum(player_hand$value) >= sum(dealer_hand$value)) {
    return(100)
  } else {
    next_vals <- deck$value + sum(player_hand$value)
    is_win <- next_vals <= 21 & next_vals >= sum(dealer_hand$value)
    return(mean(is_win) * 100)
  }
}
```

## 6. Print state

```{r}
print_game_state <- function() {
  cat('Dealer\'s hand:\n')
  for (i in 1:nrow(dealer_hand)) {
    print(glue(dealer_hand[i, "face"], 
               dealer_hand[i, "suit"], 
               dealer_hand[i, "value"], .sep = ' '))
  }
  print(glue('sum ', sum(dealer_hand$value), '\n\n'))
  
  cat('Your hand:\n')
  for (i in 1:nrow(player_hand)) {
    print(glue(player_hand[i, "face"], 
               player_hand[i, "suit"], 
               player_hand[i, "value"], .sep = ' '))
  }
  cat(glue('sum ', sum(player_hand$value), '\n\n'))
  
  cat(glue('chances ', get_chances(), '%', '\n================================\n\n\n'))
}

```


## 7. Start game function

```{r}
start_game <- function() {
  deck <<- read.csv('https://raw.githubusercontent.com/AntonZamyatin/r-course/main/HW2/deck.csv')
  shuffle_deck()
  player_hand <<- data.frame()
  dealer_hand <<- data.frame()

  give_card("dealer")
  give_card("dealer")
  give_card("player")
  give_card("player")
  
  print_game_state()
}
```

## 8. Deal function

```{r}
deal <- function() {
  give_card("player")
  
  print_game_state()
}
```

## 9. Stop game function

```{r}
stop_game <- function() {
  if (sum(player_hand$value) > 21 | sum(player_hand$value) < sum(dealer_hand$value)) {
    cat("LOSE")
  } else {
    cat("WIN")
  }
}
```

# Simulated games. Player's strategy - take cards until sum is greater or equal to 15.

# GAME 1
```{r}
start_game()
while (sum(player_hand$value) < 15) {
  deal()
}
stop_game()
```

# GAME 2
```{r}
start_game()
while (sum(player_hand$value) < 15) {
  deal()
}
stop_game()
```

# GAME 3
```{r}
start_game()
while (sum(player_hand$value) < 15) {
  deal()
}
stop_game()
```

# GAME 4
```{r}
start_game()
while (sum(player_hand$value) < 15) {
  deal()
}
stop_game()
```
